\textbf{ Normalized Gaussian Processes }

### 2020-11-24 tex/ms.tex
bugfixes
for real now
super sketchy

@@

    (n + 1) g_{n} \, \bar{\Sigma}^\frac{n+2}{2} \, \mathbf{J}_K

@@

    (n + 1) K \, g_{n} \, \mathbf{S}^\frac{n+2}{2}

@@

    n \, g_{n} \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma} + g_{n} \, \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma}

@@

            (-1)^n (n + 1)^2 g_n

@@

            \frac{K}{\mu}\left( \mathbf{S}^\frac{n+2}{2} + {\mathbf{S}^\top}^\frac{n+2}{2} \right)

@@

            \frac{n}{(n+1)\mu^2}

@@

            \mathbf{S}^\frac{n}{2} \mathbf{\Sigma}

@@

    \frac{\bar{\Sigma}}{\mu^2} & < 1

@@

>>>>

    \label{eq:SigmaTildeExp}

@@

    \frac{(n + 1) g_{n}}{\mu^{n+2}} \, \bar{\Sigma}^\frac{n+2}{2} \, \mathbf{J}_K

@@

    \frac{(n + 1) K \, g_{n}}{\mu^{n+1}} \, \mathbf{S}^\frac{n+2}{2}

@@

    \frac{g_n}{\mu^n} \left(
    n \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma} + \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma}

@@

            \frac{(-1)^n (n + 1)^2 g_n}{\mu^n}

@@

            K \left( \mathbf{S}^\frac{n+2}{2} + {\mathbf{S}^\top}^\frac{n+2}{2} \right)

@@

            \frac{1}{(n+1)}

@@

            n \mathbf{S}^\frac{n}{2}

@@

@@

However, the quantity $z^2$ is a random variable, equal to the square of
the weighted sum of $K$ standard normal random variables. The series therefore
converges only if $z^2 < 1$ for \emph{all possible values} of $z^2$, a condition
that is never strictly met except in the trivial case $\pmb{\Sigma} = \mathbf{0}$.
This may be understood intuitively: given a (very) large number of draws from
a Gaussian process, one of the draws will eventually correspond to a value of
$\mathbf{x}$ whose
mean $\bar{x}$ is arbitrarily close to zero, for which the denominators in the
expectations in Equation~(\ref{eq:SigmaTildeExp}) diverge.

While this is true for any
$\mu$ and $\pmb{\Sigma} \ne \mathbf{0}$, in practice the probability of
drawing $\bar{x} \approx 0$ is vanishingly small provided the expectation of
$z^2$ is small, a condition that may be expressed as
%
\begin{align}
    \frac{\bar{\Sigma}}{\mu^2} \ll 1
    \quad.
\end{align}
%
In this limit, any attempt to approximate $\tilde{\pmb{\Sigma}}$
numerically will yield a consistent, finite solution that
asymptotically approaches the expression derived above.
